---
title: "india webscraping"
author: "Yadu"
date: "April 23, 2016"
output: html_document
---

First, the following required packages are loaded and the working directory is set as follows. 

```{r}
library(jsonlite)
library(httr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(maptools)
library(gpclib)
library(RColorBrewer)
library(maps)
setwd("/Users/chittampalliyashaswini/Desktop/Yadu")
```

Next, the provincial data for the GINI coefficient of India is scraped as follows and then spread out. Some of the spellings of the names of the provinces have to be changed so that they will match the names listed in the shape file. 

```{r}
dat.india.province = subset(fromJSON("https://knoema.com/api/1.0/data/wiwuiff?Time=2005-2005&region=1000130,1000020,1000040,1000050,1000060,1000080,1000090,1000100,1000110,1000120,1000140,1000150,1000160,1000220,1000210,1000230,1000290,1000280,1000270,1000250&variable=1000130,1000140,1000070,1000080&Frequencies=A")$data, select = -c(Unit, Time, RegionId, Frequency, Scale))
dat.india.province = data.frame(spread(dat.india.province, variable, Value))
colnames(dat.india.province)[2:5] = c("Ruralization (Percentage)", "Urbanization (Percentage)", "RuralGini", "UrbanGini")
dat.india.province$region[8] = "Jammu and Kashmir"
dat.india.province$region[14] = "Odisha"
```

Because this dataset does not include any information for Telangana, which was formed only recently, we can just subset the data so that we get data only for the province of Andhra Pradesh and just apply it to Telangana and then order the states in alphabetic order.

```{r}
dat.telangana = data.frame(region = 'Telangana', subset(dat.india.province, region == "Andhra Pradesh", select = -c(region)))
colnames(dat.telangana) = colnames(dat.india.province)
dat.india.province = rbind(dat.india.province, dat.telangana)
dat.india.province = dat.india.province[order(dat.india.province$region),]
```

Now, for each province, we compute the GINI coefficient by weighting the rural GINI coefficient with the percentage of the rural population and the urban GINI coefficient with the percentage of the urban population.

```{r}
dat.india.province$GINI = ((dat.india.province$RuralGini)*(dat.india.province$Ruralization) + (dat.india.province$UrbanGini)*(dat.india.province$Urbanization))/100
```

The following is a linear correlation plot between urbanization and GINI coefficient for each province. 

```{r}
ggplot(dat.india.province, aes(x = `Urbanization (Percentage)`, y = GINI)) + geom_point(color = "red") + geom_smooth(method = "lm")
lm(GINI ~ `Urbanization (Percentage)`, data = dat.india.province)
summary(lm(GINI ~ `Urbanization (Percentage)`, data = dat.india.province))
```

```{r}
dat.india.province1974 = subset(fromJSON("https://knoema.com/api/1.0/data/wiwuiff?Time=1974-1974&region=1000130,1000020,1000030,1000040,1000050,1000060,1000070,1000080,1000090,1000100,1000110,1000120,1000140,1000150,1000160,1000170,1000180,1000190,1000200,1000210,1000220,1000230,1000240,1000250,1000260,1000270,1000280,1000290&variable=1000070,1000080,1000140,1000130&Frequencies=A")$data, select = c(variable, region, Value))
dat.india.province1974 = data.frame(spread(dat.india.province1974, variable, Value))
dat.india.province1974$region[7] = "Jammu and Kashmir"
dat.india.province1974$region[12] = "Odisha"
colnames(dat.india.province1974)[2:3] = c("RuralGini1974", "UrbanGini1974")
```

```{r}
dat.telangana1974 = data.frame(region = 'Telangana', subset(dat.india.province1974, region == "Andhra Pradesh", select = -c(region)))
colnames(dat.telangana1974) = colnames(dat.india.province1974)
dat.india.province1974 = rbind(dat.india.province1974, dat.telangana1974)
dat.india.province1974 = dat.india.province1974[order(dat.india.province1974$region),]

dat.chhattisgarh1974 = data.frame(region = 'Chhattisgarh', subset(dat.india.province1974, region == "Madhya Pradesh", select = -c(region))) 
colnames(dat.chhattisgarh1974) = colnames(dat.india.province1974)
dat.india.province1974 = rbind(dat.india.province1974, dat.chhattisgarh1974)
dat.india.province1974 = dat.india.province1974[order(dat.india.province1974$region),]

dat.jharkhand1974 = data.frame(region = 'Jharkhand', subset(dat.india.province1974, region == "Bihar", select = -c(region))) 
colnames(dat.jharkhand1974) = colnames(dat.india.province1974)
dat.india.province1974 = rbind(dat.india.province1974, dat.jharkhand1974)
dat.india.province1974 = dat.india.province1974[order(dat.india.province1974$region),]

dat.uttarakhand1974 = data.frame(region = 'Uttarakhand', subset(dat.india.province1974, region == "Uttar Pradesh", select = -c(region))) 
colnames(dat.uttarakhand1974) = colnames(dat.india.province1974)
dat.india.province1974 = rbind(dat.india.province1974, dat.uttarakhand1974)
dat.india.province1974 = dat.india.province1974[order(dat.india.province1974$region),]

dat.india.provincecomp = merge(dat.india.province, dat.india.province1974, by = "region")
dat.india.provincecomp$`Rural Gini Coefficient Percent Change` = (abs(dat.india.provincecomp$RuralGini-dat.india.provincecomp$RuralGini1974)/dat.india.provincecomp$RuralGini)*100
dat.india.provincecomp$`Urban Gini Coefficient Percent Change` = (abs(dat.india.provincecomp$UrbanGini-dat.india.provincecomp$UrbanGini1974)/dat.india.provincecomp$UrbanGini)*100
```

Now, we read in the shapefile for India and plot the map of India and color each province according to its GINI coefficient. 

```{r}
gpclibPermit()
gpclibPermitStatus()
map.ind.regions1 = readShapePoly("/Users/chittampalliyashaswini/Desktop/Yadu/IND_adm_shp/IND_adm1.shp", proj4string=CRS("+proj=longlat +datum=NAD27"))
map.ind.regions1 = fortify(map.ind.regions1, region = "NAME_1")
map.ind.regions1 = rename(map.ind.regions1,x=long,y=lat)

library(grid)
library(gridExtra)
mycolors = brewer.pal(9,"BrBG")
plot1 = ggplot(data=dat.india.province) + geom_map(aes(fill=GINI, map_id=region),map=map.ind.regions1) + expand_limits(map.ind.regions1) + theme_bw() + guides(fill=guide_legend(title="GINI",nrow=3,title.position="top",legend.key.width = unit(1, "cm"), title.hjust=0.5,title.theme=element_text(face="bold",angle=0))) + scale_fill_gradientn(name="Coverage", colours = mycolors) + coord_map("polyconic")

mycolors2 = brewer.pal(9,"OrRd")
plot2 = ggplot(data=dat.india.provincecomp) + geom_map(aes(fill=`Rural Gini Coefficient Percent Change`, map_id=region),map=map.ind.regions1) + expand_limits(map.ind.regions1) + theme_bw() + guides(fill=guide_legend(title="Rural GINI % Change",nrow=3,title.position="top",legend.key.width = unit(1, "cm"), title.hjust=0.5,title.theme=element_text(face="bold",angle=0))) + scale_fill_gradientn(name="Coverage", colours = mycolors2)

mycolors3 = brewer.pal(9,"Blues")
plot3 = ggplot(data=dat.india.provincecomp) + geom_map(aes(fill=`Urban Gini Coefficient Percent Change`, map_id=region),map=map.ind.regions1) + expand_limits(map.ind.regions1) + theme_bw() + guides(fill=guide_legend(title="Urban GINI % Change",nrow=3,title.position="top",legend.key.width = unit(1, "cm"), title.hjust=0.5,title.theme=element_text(face="bold",angle=0))) + scale_fill_gradientn(name="Coverage", colours = mycolors3)

grid.arrange(plot1, plot2, plot3, top = textGrob("Maps of India", gp = gpar(fontface = "bold")), ncol = 1, nrow = 3)
```

http://databank.worldbank.org/data/reports.aspx?Code=SI.POV.GINI&id=af3ce82b&report_name=Popular_indicators&populartype=series&ispopular=y

http://gis.stackexchange.com/questions/102781/chloropeth-map-in-r-data-on-map-not-represented-as-in-listed-in-the-file